Human capital mediates natural selection in contemporary humans

### 2022-12-09 why-natural-selection.Rmd
get back to published version of paper

res_mediation %>%
      arrange(desc(estimate_total)) %>%
      transmute(
        PGS = pretty_names(term),
        `Total effect`    = estimate_total,
        `Indirect effect` = paste(estimate_ind, star),
        `Proportion (%)`      = prop_ind * 100,
        `Proportion 95% c.i. (%)` = glue::glue(
                     "[{prop_ind_conf_low * 100}, {prop_ind_conf_high * 100}]"
                     )
      ) %>%
      as_hux() %>%
      set_align(everywhere, -1, "right") %>% 
      set_number_format(-1, 2:3, 4) %>% 
      set_number_format(-1, 4:5, 1) %>% 
      set_caption("Mediation analysis") %>% 
      theme_compact() %>% 
      set_width(0.95) %>%
      set_col_width(c(.25, .15, .15, .15, .25)) %>% 
      set_bottom_border(final(), everywhere) %>%
      set_font_size(9) %>% 
      add_footnote(footnote, font_size = 8)
```

Table \@ref(tab:tbl-res-mediation) shows results. For `r n_pos_sig` out of 
`r n_regs` scores, the indirect effect on fertility via human capital is
significantly different from 0 at $p$ = 0.05/`r n_regs` and has the same sign
as the total effect. We also calculate the proportion of the total effect that
is mediated via the indirect effect, along with uncorrected 95% confidence
intervals (100 bootstraps).

>>>>

res_mediation %>%
      arrange(desc(estimate_total)) %>%
      transmute(
        PGS = pretty_names(term),
        `Total effect`    = estimate_total,
        `Indirect effect` = paste(estimate_ind, star),
        `Proportion (%)`  = prop_ind * 100,
        bounded_ci        = sign(estimate_total_conf_low) ==
                              sign(estimate_total_conf_high),
        `Proportion 95% c.i. (%)` = glue::glue(
                     "[{prop_ind_conf_low * 100}, {prop_ind_conf_high * 100}]"),
        `Proportion 95% c.i. (%)` = ifelse(bounded_ci, 
                                             `Proportion 95% c.i. (%)`,
                                             "Unbounded")
      ) %>% 
      select(-bounded_ci) %>%
      as_hux() %>%
      set_align(everywhere, -1, "right") %>% 
      set_number_format(-1, 2:3, 4) %>% 
      set_number_format(-1, 4:5, 1) %>% 
      set_caption("Mediation analysis") %>% 
      theme_compact() %>% 
      set_width(0.95) %>%
      set_col_width(c(.25, .15, .15, .15, .25)) %>% 
      set_bottom_border(final(), everywhere) %>%
      set_font_size(9) %>% 
      add_footnote(footnote, font_size = 8)
```

Table \@ref(tab:tbl-res-mediation) shows results. For `r n_pos_sig` out of 
`r n_regs` scores, the indirect effect on fertility via human capital is
significantly different from 0 at $p$ = 0.05/`r n_regs` and has the same sign
as the total effect. We also calculate the proportion of the total effect that
is mediated via the indirect effect, along with uncorrected 95% confidence
intervals (100 bootstraps). Note that if the confidence interval for the total
effect contains zero, the confidence interval for the proportion may be unbounded
[@franz2007ratios].
